Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-26 Documents/FP in NAGs/neurips_2021.tex
Updated Section 4

In this study, we investigate a variant of the aggregative game known as the \emph{Network
Aggregative} (NA) Game. This format assumes that each agent updates their actions according only to those agents with whom they are connected on an underlying network. This significantly relaxes the communication load on each agent and
lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the previous behaviour of the others.

@@

The NA game is a recent introduction \cite{Parise2015} which presents
a variant of aggregative games by adding an underlying structure to
the population. Since its introduction, distributed algorithms have
been built with the aim of finding NE. In particular,
\cite{Parise2015, Parise2020} consider the case in which payoffs are
given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will
converge to the NE. Another approach for distributed NE seeking is the
projected gradient (resp. subgradient) dynamics which is explored in
\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
works, the cost function is assumed to be convex, and therefore have a
unique minimiser. In fact this is a common assumption in works
concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due
to its ubiquity in control settings. We have not yet come across works
which consider NA games from the point of view of payoff matrices,
which are more common in multi-agent learning settings.  Furthermore,
to the best of our knowledge, this is the first work which introduces
the application of a learning algorithm in the NA setting.

@@

Then, the agent must optimise their payoff with respect to the
reference vector $\sigma^{\mu}$. Thus, instead of considering
the actions of the entire population, or play individual games
against each of their neighbours, the agent only considers
$\sigma^\mu$ as a `measurement' of the local aggregate state and
optimises with respect to this measurement.  This allows us to make
the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
particular, we consider that the agent is engaged in a matrix game
against the reference vector so that
%
\begin{equation}
	u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
	\cdot A^\mu \weightedsum.
\end{equation}
%
where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can write the game $\Gamma$ with the payoff
matrices $A^\mu$ in place of the utility functions
$\utility{\mu}$. Hence, the NA game allows for the reduction of a
multi-player game into a series of two-player games. The agent's goal
is to maximise their payoff with respect to the reference vector. As
such, we define the best response correspondence $BR^\mu$, which maps
every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
	\refmu)}$.

Finally, a central concept of game theory is that of the Nash
Equilibrium, in which no rational agent has the incentive to deviate
from their current state. This can be formalised by saying that all
agents are playing their best response to each other.
%
This leads naturally to the definition of a Nash Equilibrium in an NA game as
%
\begin{definition}(NE) \label{def::NE}
	The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is a {\em
		Nash equilibrium} if, for all $\mu$,
	\begin{equation*}
		\NE{\mu} \in BR^\mu (\refmu) = \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
	\end{equation*} 
\end{definition}

\begin{remark}
	%It can be seen that
	The notion of Nash equilibrium in the NA game is a natural
	extension of the NE in a bimatrix game.
	%$(A, B)$.
	In particular, if we consider an NA game with only two players and no
	self-loops then the above definition yields that $ \NE{1}$ is an NE iff
	%
	%    \begin{equation*}
	$     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2})$,
	%    \end{equation*}
	%
	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
\end{remark}

@@

  Using this, we follow in the footsteps of  \cite{Ewerhart2020} and \cite{Harris1998} to define
  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
%
  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)] \label{def::NACTFP}
    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
    and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
  \end{definition}

  We can think of this definition as saying that the player plays some arbitrary strategy before
  $t = 1$, but beyond this it must play a best response to the time average of its reference
  signal.

  \begin{remark}
    As an illustration, consider the NA game with two players, in which $\edgeset = \{(1, 2),
    (2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
    the off diagonal. We write the time-average of both agents' state as

    \begin{align}
      \alpha^\mu(t; x) = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
  %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
    \end{align}

@@

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that the Fictitious Play
  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?} \ah{So the existence of the NE and the FP dynamic are independent of one another. The NE is a property of the game only, whereas FP is a separate differential equation (12 in the supplementary material). Whilst it is intuitive that the solutions to (S12) exists, on a technical sense we still have to prove it.}. Finally, we show that NA-CTFP reaches a fixed point when
  the NA game is zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & \stackrel{\text{def}}{=} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

@@

  \begin{lemma}
    There exists a path $m(t)$ which satisfies the property that, for all agents $\mu$, $m^\mu(t) \in
    BR^\mu(\alpha_\sigma^\mu(t))$ for almost all $t \geq 1$.
  \end{lemma}

@@

  In the proof of Theorem \ref{thm::NACTFPtoFixed} it can be seen that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the fixed point corresponds to an NE. In particular Eqn. (26) in the supplementary materal corresponds to the NE condition when $w^{\mu \mu} = 0$. This leads to the next result.
%
  \begin{corollary} \label{thm::NACTFPtoNE}
    With the additional assumption that $w^{\mu \mu} = 0$ for all agents $\mu$, all zero-sum NA games have the property that any NA-CTFP path converges to the set of Nash Equilibria.
  \end{corollary}

@@

  In this section we aim to understand the long term behaviour of NA-CTFP for the
  case in which the NA game is not necessarily zero-sum. In
  particular, we show that the NA-CTFP process converges to the set of
  coarse correlated equilibria \cite{Nisan2007}.
  %
  \begin{definition}[CCE]
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
     if, for all $\mu$
    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

  In words, the above definition says that, if the agents are given a
  probability distribution with which they can play their actions, then
  the expected payoff, for all agents is greater than or equal to the
  payoff that they would get by playing any of their other available
  actions, assuming that the other agents keep to the distribution.

  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is
  drawn from a joint probability distribution $\mathcal{D}$, then
  there is a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
  distribution over both the actions and the references.  Consider, then, a
  vector of joint distributions over actions and references which is
  generated by NA-CTFP. In particular, if by playing with NA-CTFP, the
  agents reach state $(\xmu)_{i = 1}^N$ with references
  $(\refmu)_{i = 1}^N$, $\mathcal{D} =
  (\mathcal{D}^1, ..., \mathcal{D}^N)$ is such that
  $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
  payoff that the agent would receive for playing this strategy is
%
  \begin{align*}
    u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
  \end{align*}

  As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
  \rightarrow \infty$, we have that for all agents $\mu$,
%  \begin{equation}
  $u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu)$
  %\hspace{1cm} \
  for all $i' \in S^\mu$.
%  \end{equation}

@@

  \begin{remark} \label{rem::regretvsCCE}
    The notion of the CCE set is related to the idea of \emph{average regret}  \cite{Nisan2007}. Here, we
    will present what is meant by average regret and state that if at some time $T$ all agents'
    average regret is non-positive, then the game is said to have reached the CCE set. The
    reader should consult \cite{Ostrovski2014} for an excellent exposition regarding the
    link between the CCE set and average regret in two player games which, of course, extends
    naturally to the NA game.

    Average regret, for agent $\mu$ is defined as
%
    \begin{equation}
      R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(\pure{\mu}{i'}, \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\},
    \end{equation}

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by
%    
    \begin{equation}
      u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
    \end{equation}

@@

    \begin{equation}
      u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
    \end{equation}

@@

  \begin{theorem} \label{thm::NACTFPtoCCE}
    Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the
    NA-CTFP process achieve \emph{no regret} in the limit $t \rightarrow \infty$, i.e.
    \begin{equation}
      \lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
    \end{equation}

@@

  As an adaptation, we take the example of a three player chain, in which player $2$ is connected to $1$ and $3$. The aggregation matrix can be given as
%
  \begin{equation}
    W = \begin{bmatrix}
      0 & 1 & 0 \\
      w & 0 & 1 - w \\
      0 & 1 & 0
    \end{bmatrix}, \; w \in (0, 1).
  \end{equation}

>>>>

In this study, we investigate a variant of the aggregative game known as the \emph{Network
Aggregative} (NA) Game. This format assumes that each agent updates their actions according only to those agents with whom they are connected on an underlying network. This significantly relaxes the communication load on each agent and
lifts the need for a central coordinator. Recent work on NA games has shown that it is possible
for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the previous behaviour of the others.

@@

NA games are a recent introduction \cite{Parise2015} which presents
a variant of aggregative games by adding an underlying structure to
the population. Since its introduction, distributed algorithms have
been built with the aim of finding NE. In particular,
\cite{Parise2015, Parise2020} consider the case in which payoffs are
given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will
converge to the NE. Another approach for distributed NE seeking is the
projected gradient (resp. subgradient) dynamics which is explored in
\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
works, the cost function is assumed to be convex, and therefore have a
unique minimiser. In fact this is a common assumption in works
concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due
to its ubiquity in control settings. We have not yet come across works
which consider NA games from the point of view of payoff matrices,
which are more common in multi-agent learning settings.  Furthermore,
to the best of our knowledge, this is the first work which introduces
the application of a learning algorithm in the NA setting.

@@

Then, the agent must optimise their payoff with respect to the
reference vector $\sigma^{\mu}$. Thus, instead of considering
the actions of the entire population, or play individual games
against each of their neighbours, the agent only considers
$\sigma^\mu$ as a `measurement' of the local aggregate state and
optimises with respect to this measurement.  This allows us to make
the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
particular, we consider that the agent is engaged in a matrix game
against the reference vector so that
%
\begin{equation}
	u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
	\cdot A^\mu \weightedsum.
\end{equation}
%
where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can write the game $\Gamma$ with the payoff
matrices $A^\mu$ in place of the utility functions
$\utility{\mu}$. Hence, NA Games allow for the reduction of a
multi-player game into a series of two-player games. The agent's goal
is to maximise their payoff with respect to the reference vector. As
such, we define the best response correspondence $BR^\mu$, which maps
every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
	\refmu)}$.

Finally, a central concept of game theory is that of the Nash
Equilibrium, in which no rational agent has the incentive to deviate
from their current state. This can be formalised by saying that all
agents are playing their best response to each other.
%
This leads naturally to the definition of a Nash Equilibrium in an NA game as
%
\begin{definition}(NE) \label{def::NE}
	The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is a {\em
		Nash equilibrium} if, for all agents $\mu$,
	\begin{equation*}
		\NE{\mu} \in BR^\mu (\refmu) = \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
	\end{equation*} 
\end{definition}

\begin{remark}
	%It can be seen that
	The notion of Nash equilibrium in NA Games is a natural
	extension of the NE in a bimatrix game.
	%$(A, B)$.
	In particular, if we consider an NA game with only two players and no
	self-loops then the above definition yields that $ \NE{1}$ is an NE iff
	%
	%    \begin{equation*}
	$     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2})$,
	%    \end{equation*}
	%
	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
\end{remark}

@@

  Using this, we follow in the footsteps of  \cite{Ewerhart2020} and \cite{Harris1998} to define
  Fictitious Play in continuous time, but with a slight adaptation for NA Games.
%
  \begin{definition}[Fictitious Play on Network Aggregative Games] \label{def::NACTFP}
    We define Continuous Time Fictitious Play on Network Aggregative Games as a measurable map $m$ with components $m^\mu$ such that for all agents $\mu$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all time $t \geq 1$. Henceforth, $m$ will be called an \emph{NA-CTFP}.
  \end{definition}

  We can think of this definition as saying that the player plays some arbitrary strategy before
  $t = 1$, but beyond this it must play a best response to the time average of its reference
  signal. We also refer to this measurable map as a `path'. In Section \ref{sec::CTFPAnalysis}, we prove that a path $m$ which satisfies this definition exists.

  \begin{remark}
    As an illustration, consider NA Games with two players, in which $\edgeset = \{(1, 2),
    (2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
    the off diagonal. We write the time-average of both agents' state as

    \begin{align*}
      \alpha^\mu(t; x) = \frac{1}{t} \int_0^t \xmu(s) \, ds & \text{ for $\mu \in \{1, 2\}$}
  %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
    \end{align*}

@@

  In this section we present our main results. First, we establish the
  existence of a Nash equilibrium in NA games, as defined in
  Def.~\ref{def::NE}. Then we show that an NA-CTFP (i.e. a path $m$ which satisfies Def.~\ref{def::NACTFP}) exists. Finally, we show that NA-CTFP reaches a fixed point when
  NA Games are zero-sum and that, when the network has no self-loops
  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
  of brevity, we defer the proofs of our statements, as well as the
  standard topological arguments used to derive them, to the
  supplementary material (Sections (S4 - S6)).

  As a reminder,
  %the NE condition (
  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
%
  \begin{align*}
    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
  \end{align*}
%
  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other agent states $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
%  
  \begin{align}
    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
     & \stackrel{\text{def}}{=} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
  \end{align}
%  
  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.

@@

  \begin{lemma}
    There exists a path $m(t)$ which satisfies the property that, for all agents $\mu$, $m^\mu(t) \in
    BR^\mu(\alpha_\sigma^\mu(t))$ for almost all times $t \geq 1$.
  \end{lemma}

@@

  In the proof of Theorem \ref{thm::NACTFPtoFixed} it can be seen that, if we choose $w^{\mu \mu}$ to be zero for all agents $\mu$, then the fixed point corresponds to an NE. In particular Eqn. (26) in the supplementary materal corresponds to the NE condition when $w^{\mu \mu} = 0$. This leads to the next result.
%
  \begin{corollary} \label{thm::NACTFPtoNE}
    With the additional assumption that $w^{\mu \mu} = 0$ for all agents $\mu$, all zero-sum NA games have the property that any NA-CTFP path converges to the set of Nash Equilibria.
  \end{corollary}

@@

  In this section we aim to understand the long term behaviour of NA-CTFP for the
  case in which NA games are not necessarily zero-sum. To do this, we first introduce the coarse correlated equilibria (CCE) \cite{Nisan2007} in the context of NA games as a natural extension to the two-player case. Then, we show that the NA-CTFP process converges to the set of
  CCE
  %
  \begin{definition}[CCE] \label{def::CCE}
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
     if, for all agents $\mu$, $
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})]$ $ \forall j \in S^\mu.$
  \end{definition}

  In words, the above definition says that, if the agents are given a
  probability distribution with which they can play their actions, then
  the expected payoff, for all agents, is greater than or equal to the
  payoff that they would get by playing any of their other available
  actions, assuming that the other agents keep to the distribution.

  For an NA game, a set of actions $s = (s^1, \ldots, s^N)$ which is
  drawn from a joint probability distribution $\mathcal{D}$, also generates
  a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$. In other words, if we draw $s$ from $\mathcal{D}$, then we have also drawn $\sigma$, which means our CCE condition, Def.~\ref{def::CCE}, can be written as $
\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] \geq
\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, \refmu)]$ $ \forall j \in S^\mu$ and all agents $\mu$.

  Now, if by playing with NA-CTFP, the
  agents reach state $(\xmu)_{i = 1}^N$ with references
  $(\refmu)_{i = 1}^N$, then we can define a distribution $\mathcal{D} =
  (\mathcal{D}^1, ..., \mathcal{D}^N)$ so that
  $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
  payoff that the agent would receive for playing this strategy is
%
  \begin{align*}
    \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] = u^\mu (\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
  \end{align*}

  As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
  \rightarrow \infty$, we have that for all agents $\mu$,
%  \begin{equation}
  $u^\mu (\xmu, \refmu) \geq u^\mu(j, \refmu)$
  %\hspace{1cm} \
  for all actions $j \in S^\mu$.
%  \end{equation}

@@

  \begin{remark} \label{rem::regretvsCCE}
    The notion of the CCE set is related to the idea of \emph{average regret}  \cite{Nisan2007}. Here, we
    will present what is meant by average regret and state that if at some time $t$ all agents'
    average regret is non-positive, then the game is said to have reached the CCE set. The
    reader should consult \cite{Ostrovski2014} for an excellent exposition regarding the
    link between the CCE set and average regret in two player games which, of course, extends
    naturally to NA Games.

    Average regret, for agent $\mu$ is defined as
%
    \begin{equation*}
      R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{t} \int_{0}^{t} u^{\mu}(\pure{\mu}{i'}, \sigma(s)) - u^{\mu}(m^\mu(s), \sigma(s)) \, ds \Big\},
    \end{equation*}

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by
%    
    \begin{equation*}
      u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
    \end{equation*}

@@

    \begin{equation*}
      u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
    \end{equation*}

@@

  \begin{theorem} \label{thm::NACTFPtoCCE}
    Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the
    NA-CTFP process achieve \emph{no regret} in the limit $t \rightarrow \infty$, i.e.
    \begin{equation}
      \lim_{t \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{t} \int_{0}^{t} u^{\mu}(x_{i'}^\mu(s), \sigma(s)) - u^{\mu}(m^\mu(s), \sigma(s)) \, ds \Big\} = 0
    \end{equation}

@@

  As an adaptation, we take the example of a three player chain, in which player $2$ is connected to $1$ and $3$. The aggregation matrix can be given as
%
  \begin{equation*}
    W = \begin{bmatrix}
      0 & 1 & 0 \\
      w & 0 & 1 - w \\
      0 & 1 & 0
    \end{bmatrix}, \; w \in (0, 1).
  \end{equation*}
